Trends of SDR in Thessaloniki

### 2023-07-13 Build_151/Article_B151.Rmd
Commit 2023-07-13 08:09

.......!!!.......

### Aggregation of radiometric data

<!-- aggregation -->
Before further analysis and deseasonalization, we implement an appropriate aggregation scheme on the 1-minute data. To preserve the representativeness we use the following criteria:
a) for daily mean values we exclude instances with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily aggregated data, where months with less than `r Monthly_aggegation_N_lim` days are rejected. 
The daily seasonal values were indexed based on the day of year number, and the monthly by the corresponding calendar month.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by season (Winter: December - February, Spring: March - May, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation.
This is done, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
<!-- SZA Deseasonalization -->
In addition to the previous aggregation scheme, each dataset was aggregate in $1^\circ$ SZA bins, separate for cases before and after local noon. 
This gave us an approximation of Sun's SZA contribution to the SDR brightening.

Thus, for each data set we have obtained the relative departure of the seasonal mean.
The statistical significance and aggregation scheme and filtering will be noted along with the corresponding results.

>>>>

<!-- aggregation -->
In order to investigate the SDR trend, we implement an appropriate aggregation scheme of the 1-minute data to a coarser time scale. To preserve the representativeness we are using the following criteria:
a) for daily mean values we exclude days with less than `r Daily_aggregation_N_lim` valid data points,
b) accordingly, monthly values are computed by daily means, and months with less than `r Monthly_aggegation_N_lim` days are omitted. 
To create the daily and monthly seasonal values, we group the data based on the day of year number, and the corresponding calendar month respectively.
<!-- Seasonal -->
For the seasons of the year trends, we grouped the mean daily values by the corresponding season (Winter: December - February, Spring: March - May, etc.).
<!-- Deseasonalization -->
Finally, for each data set, we remove the natural occurring seasonal variation, by calculating the mean values for the appropriate time step, and subtracting the annual cycle from the actual data.
<!-- SZA Deseasonalization -->
To estimate Sun's SZA contribution to the SDR brightening, the 1-minute data were aggregate in $1^\circ$ SZA bins, separated for instances before and after the local noon, and then was deseasonalized as above. 
Thus, for each dataset we have obtained the relative departure of the seasonal mean.
